\LaTeX\ Author Guidelines for 3DIMPVT Proceedings

### 2012-06-20 3dimpvt/paper.tex
draft 1 ready i hope

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

@@

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

@@

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ifcvprfinal\pagestyle{empty}\fi
\begin{document}

@@

\begin{figure}
  \centering
  \includegraphics[height=1.5in]{scoringFunction.pdf}
  \caption{For each tile, we find the image that minimizes $d$ and $\alpha$ by maximizing the following equation: $(1/d \cdot (-1 \cdot C) \cdot N)$}
  \label{fig:scoringFunction}
\end{figure}

@@

@@

\subsection{Localized Mapping with Caching}
In figure \ref{fig:shifted}, we see the same wall from section 3,
texture mapped using the caching method, both without and with
localization for comparison.

@@

It should be evident that our localization adjustments resulted in a
major improvement. A great strength of our tiling approach for image
selection is that it runs regardless of plane geometry or orientation,
and can handle images of all types. For example, here is the approach
as run on a ceiling and floor plane, both of which contain a multitude
of non-optimal images due to the camera locations on the backpack.

% \begin{figure}
%   \centering
%   \includegraphics[width=3in]{localized_caching_ceiling.png}
%   \caption{Using the graph-based localization refinement algorithm
%   from [11] suffers from the problem of compounding errors. }
%   \label{fig:graph}
% \end{figure}

Given that the backpack system's hardware and the data collection
process do strive to collect optimal images for walls however, we can
be less reserved when texturing walls, and simply fall back to this
more robust approach as needed.

\subsection{Texture Mapping with Seam Minimization}
The cached tile approach selected images based on individual quality
and neighboring quality, in an effort to reduce seams between
tiles. In a more optimal case, as the backpack system provides for
walls, images all have near-rectangular projections and thus a great
score according to the scoring function in figure
\ref{fig:scoringFunction}. Thus, we can reason that rather than
selecting the set of best images, since all images are good, we should
instead select the best set of images, such that the selection results
in the cleanest texture possible. We will accomplish this by using
entire images where possible, defining a cost function between images,
and seeking to maximize our total cost.

@@

%\begin{figure}
%  \centering
%  \includegraphics[width=3in]{DynProg.pdf}
%  \caption{Image Selection is done by constructing a graph of sorted
%    images. Then we solve a shortest path problem where the edge
%    weights represent the cost of a seam between two overlapping
%    images.}
%  \label{fig:DynProg}
%\end{figure}

Figure \ref{fig:DynProg} demonstrates the construction of a DAG from
overlapping images of a long hallway. Images are sorted by horizontal
location left to right, and become nodes in a graph. Directed edges
are placed in the graph from left to right between images that
overlap. The weights of these edges are determined by the cost
functions discussed previously. Next, we add two artificial nodes, one
start node representing the left border of the plane, and one end node
representing the right border of the plane. The left artificial node
has directed edges with equal cost to all images that meet the left
border of the plane, and the right artificial node has directed edges
from all images that meet the right border of the plane.

@@

With this completed, we have now mapped every location on our plane to
at least one image, and have minimized the amount of images, as well
as the discontinuity between their borders. In the next section, we
will apply blending between images where they overlap, but for the
sake of comparison with the unblended tile caching method in section
5.1, we arbitrarily pick one image for texturing where images
overlap. The following images compare the tile caching method against
this seam minimization method.

%\begin{figure}
%  \centering
%  \includegraphics[height=2in]{compare_wall.png}
%  \caption{Planes are specified in 3D space by four corners $C_1$ to
%    $C_4$. Images are related to each plane through the camera
%    matrices $P_{1..M}$. }
  % \caption{The plane is specified in 3D space by the four corners
  % $C_1$ to $C_4$. Images are related to the plane through the camera
  % matrices $P_{1..M}$. For example, the 3D point X in the world
  % coordinate system is related to the image point x shown in the
  % figure as $x = P_i X$.}
%  \label{fig:compare_wall}
%\end{figure}

Though both methods provide quite accurate texturing thanks to the
localization refinement process, the seam minimization approach
results in fewer visible discontinuities, since it directly reduces
the cost of each image boundary, while the tile caching method uses a
scoring function that only approximates this effect. Furthermore, seam
minimization guarantees the best selection of images, while the tile
caching method may select images early on that turn out to be poor
choices once subsequent tiles have been processed. This can be a
problem when localization refinement does not work perfectly. Such an
effect can be seen in the following image.

In the context of the backpack modeling system, we apply the seam
minimization approach on walls, due to its superior output when
provided with optimal images. Floors and ceilings however, given their
suboptimal images which require segmentation, are textured using the
tile caching method.

@@

Our alpha blending technique is widely used, and blends pixels
linearly across overlapping regions. For each pixel within such a
region, we simply scale its intensity (by a factor from 0 to 1),
based on its distance from the image's border, with a cap set at a fixed distance from the border. In this way, we interpolate between two
overlapping images, providing a gradual transition between
them. Increasing the blending distance results in a
smoother transition, but can also result in more blurriness. A blended and unblended version of each method is shown below for comparison.

%\begin{figure}
%5  \centering
 % \includegraphics[height=2in]{compare_blending.png}
%  \caption{Planes are specified in 3D space by four corners $C_1$ to
%    $C_4$. Images are related to each plane through the camera
%    matrices $P_{1..M}$. }
%  % \caption{The plane is specified in 3D space by the four corners
  % $C_1$ to $C_4$. Images are related to the plane through the camera
  % matrices $P_{1..M}$. For example, the 3D point X in the world
  % coordinate system is related to the image point x shown in the
  % figure as $x = P_i X$.}
%  \label{fig:compare_blending}
%\end{figure}

\section{Conclusion and Results}
In this paper, we have shown how to accurately texture map models,
even when provided with imprecise camera localization data. We have
generalized one approach to any manner of planes and images, and
successfully textured both simple rectangular walls as well as complex
floor and ceiling geometry. We have also presented an optimized
texturing method that takes advantage of our localization refinement
process and produces cleaner textures on planes where multiple head-on
images are available. Ceilings and floors textured with the robust
approach, and walls textured with the optimized approach, are
displayed in the remainder of this paper. A more detailed walkthrough
demonstrating fully textured models using the approaches in this paper
can be seen in the accompanying video to this paper.

>>>>

\usepackage{cvpr} \usepackage{times} \usepackage{epsfig}
\usepackage{graphicx} \usepackage{amsmath} \usepackage{amssymb}
\usepackage{subfig}

@@

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first
% latex run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

@@

% Pages are numbered in submission mode, and unnumbered in
% camera-ready
\ifcvprfinal\pagestyle{empty}\fi
\begin{document}

@@

\begin{figure}
  \centering
  \includegraphics[height=1.5in]{scoringFunction.pdf}
  \caption{For each tile, we find the image that minimizes $d$ and
    $\alpha$ by maximizing the following equation: \\ $(1/d \cdot (-1
    \cdot C) \cdot N)$}
  \label{fig:scoringFunction}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=3in]{matches.jpg}
  \caption{SIFT feature matches between overlapping images.}
  \label{fig:matches}
\end{figure}

@@

\subsection{Localized Mapping with Caching}
In figure \ref{fig:shifted}, we see the same wall from section 3,
texture mapped using the caching method after our localization
refinement process.

@@

It should be evident that our localization adjustments resulted in a
major improvement. A great strength of our tiling approach for image
selection is that it extracts the areas with good camera angles from
each image, and thus can handle images of all types. As demonstrated
on the floor plane in figure \ref{fig:floor_suboptimal}, we can run
this process even with extremely poor image projections, where the
amount of quality texture for each image is limited. Additionally,
since our plane is discretized, we can easily handle arbitrarily
complex planes as well.

\begin{figure}
  \centering
  \includegraphics[width=3in]{floor_suboptimal.jpg}
  \caption{The tiling method ensures that only the most optimal
    portions of each image are used. This allows it to successfully
    handle all manner of plane and image geometry, as shown in this
    floor texture.}
  \label{fig:floor_suboptimal}
\end{figure}

Given that the backpack system's hardware and the data collection
process strive for optimal wall texturing however, we can aim for a
less conservative approach when texturing walls, and simply fall back
to this more robust approach as needed.

\subsection{Texture Mapping with Seam Minimization}
The cached tile approach selected images based on individual and
neighboring quality of image selections, in an effort to reduce seams
between tiles. In a more optimal case, as the backpack system provides
for walls, images are all taken from close distances and have
near-rectangular projections and thus a great score according to the
scoring function in figure \ref{fig:scoringFunction}. Thus, we can
reason that rather than selecting the set of best images, since all
images are good, we should instead select the best set of images, such
that the selection together results in the cleanest final texture. We
will accomplish this by using entire images where possible, defining a
cost function between images, and seeking to minimize our total cost.

@@

\begin{figure}
  \centering
  \includegraphics[width=3in]{dagCreation.pdf}
  \caption{DAG construction for the image selection process.}
  \label{fig:dagCreation}
\end{figure}

Figure \ref{fig:dagCreation} demonstrates the construction of a DAG
from overlapping images of a long hallway. Images are sorted by
horizontal location left to right, and become nodes in a
graph. Directed edges are placed in the graph from left to right
between images that overlap. The weights of these edges are determined
by the cost functions discussed previously. Next, we add two
artificial nodes, one start node representing the left border of the
plane, and one end node representing the right border of the
plane. The left artificial node has directed edges with equal cost
$C_0$ to all images that meet the left border of the plane, and the
right artificial node has directed edges from all images with that
meet the right border of the plane, with equal cost $C_0$ as well.

@@

With this completed, we have now mapped every location on our plane to
at least one image, and have minimized the amount of images, as well
as the discontinuity between their borders. In the next section, we
will apply blending between images where they overlap, but for the
sake of comparison with the unblended tile caching method in section
5.1, we arbitrarily pick one image for texturing where images
overlap. Figure \ref{fig:compare_unblended} compares the tile caching
method against this seam minimization method.

\begin{figure}
  \centering
  \includegraphics[width=3in]{wall1_cache_full_shifted.jpg}
  \includegraphics[width=3in]{wall1_dynprog_noblend.jpg}
  \caption{The tile caching approach is presented above the seam
    minimization approach.}
  \label{fig:compare_unblended}
\end{figure}

Though both methods provide quite accurate texturing thanks to the
localization refinement process, the seam minimization approach
results in fewer visible discontinuities, since it directly reduces
the cost of each image boundary, while the tile caching method uses a
scoring function that only approximates this effect. Furthermore, seam
minimization guarantees the best selection of images, while the tile
caching method may select images early on that turn out to be poor
choices once subsequent tiles have been processed.

In the context of the backpack modeling system, we apply the seam
minimization approach on walls, due to its superior output when
provided with optimal images. Floors and ceilings however, given their
suboptimal images, as shown in figure \ref{fig:floor_suboptimal}, can
only be textured using the tile caching method.

@@

Our alpha blending technique is widely used, and blends pixels
linearly across overlapping regions. For each pixel within such a
region, we simply scale its intensity (by a factor from 0 to 1), based
on its distance from the image's border, with a cap set at a fixed
distance from the border. In this way, we interpolate between two
overlapping images, providing a gradual transition between them. Our
texture mapping process is now complete, and in figure
\ref{fig:pipeline}, we review our entire pipeline and demonstrate the
final blended output of both approaches.

\begin{figure}
  \centering
  \includegraphics[width=3in]{pipeline.pdf}
  \caption{Our final texture processing pipeline, with the final
    output of both approaches.}
  \label{fig:pipeline}
\end{figure}

\section{Conclusion and Results}
In this paper, we have shown how to accurately texture map models,
even when provided with imprecise camera localization data. We have
generalized one approach to any manner of planes and images, and
successfully textured both simple rectangular walls as well as complex
floor and ceiling geometry. We have also presented an optimized
texturing method that takes advantage of our localization refinement
process and produces cleaner textures on planes where multiple head-on
images are available. Ceilings and floors textured with the robust
approach, and walls textured with the optimized approach, are
displayed in figure \ref{fig:results}. A more detailed walkthrough
demonstrating fully textured 3D models using the approaches in this
paper is available in the accompanying video to this paper.

\begin{figure}
  \centering
  \includegraphics[width=3in]{4thfloor21.jpg}
  \includegraphics[width=3in]{4thfloor61.jpg}
  \includegraphics[width=2in]{4thfloor8.jpg}
  \includegraphics[width=3in]{fullmodel.png}
  \caption{Examples of our final texture mapping output for walls, floors, and ceilings}
  \label{fig:results}
\end{figure}
